

```{r}

a1 <- readRDS(here::here("RData", "050-all_pairs_df_initial.rds"))
a2 <- readRDS(here::here("RData", "050-all_pairs_df_consensus.rds"))
```

# Rater agreement

```{r}
#| label: correlation
# Compute and format correlation coefficient
corr_delirium_severity_initial <- cor(a1$delirium_severity_A, a1$delirium_severity_B, use = "complete.obs")
corr_delirium_severity_initial <- formatC(corr_delirium_severity_initial, digits = 2)
corr_delirium_severity_consensus <- cor(a2$delirium_severity_A, a2$delirium_severity_B, use = "complete.obs")
corr_delirium_severity_consensus <- formatC(corr_delirium_severity_consensus, digits = 2)

corr_delirium_presence_initial <- cor(a1$delirium_presence_A, a1$delirium_presence_B, use = "complete.obs")
corr_delirium_presence_initial <- formatC(corr_delirium_presence_initial, digits = 2)
corr_delirium_presence_consensus <- cor(a2$delirium_presence_A, a2$delirium_presence_B, use = "complete.obs")
corr_delirium_presence_consensus <- formatC(corr_delirium_presence_consensus, digits = 2)

corr_dementia_severity_initial <- cor(a1$dementia_severity_A, a1$dementia_severity_B, use = "complete.obs")
corr_dementia_severity_initial <- formatC(corr_dementia_severity_initial, digits = 2)
corr_dementia_severity_consensus <- cor(a2$dementia_severity_A, a2$dementia_severity_B, use = "complete.obs")
corr_dementia_severity_consensus <- formatC(corr_dementia_severity_consensus, digits = 2)

corr_ncd_presence_initial <- cor(a1$ncd_presence_A, a1$ncd_presence_B, use = "complete.obs")
corr_ncd_presence_initial <- formatC(corr_ncd_presence_initial, digits = 2)
corr_ncd_presence_consensus <- cor(a2$ncd_presence_A, a2$ncd_presence_B, use = "complete.obs")
corr_ncd_presence_consensus <- formatC(corr_ncd_presence_consensus, digits = 2)
```

```{r}
#| label: kappa
# Compute and format kappa statistic
my_kappa_fx <- function(df, x1, x2) {
  x <- df %>%
    select(all_of(c(x1, x2))) %>%
    table()
  y <- psych::cohen.kappa(x)
  k <- y$weighted.kappa %>% round(2)
  ci_l <- y$confid[2, 1] %>% round(2)
  ci_u <- y$confid[2, 3] %>% round(2)
  str_c(k, " (", ci_l, ", ", ci_u, ")")
}
kap_delirium_presence_initial   <- my_kappa_fx(a1, "delirium_presence_A", "delirium_presence_B")
kap_delirium_presence_consensus <- my_kappa_fx(a2, "delirium_presence_A", "delirium_presence_B")

kap_delirium_severity_initial   <- my_kappa_fx(a1, "delirium_severity_A", "delirium_severity_B")
kap_delirium_severity_consensus <- my_kappa_fx(a2, "delirium_severity_A", "delirium_severity_B")

kap_ncd_presence_initial   <- my_kappa_fx(a1, "ncd_presence_A", "ncd_presence_B")
kap_ncd_presence_consensus <- my_kappa_fx(a2, "ncd_presence_A", "ncd_presence_B")

kap_dementia_severity_initial   <- my_kappa_fx(a1, "dementia_severity_A", "dementia_severity_B")
kap_dementia_severity_consensus <- my_kappa_fx(a2, "dementia_severity_A", "dementia_severity_B")

```

## Delirium severity

```{r}
#| label: tbl-delseverity-cross-pre
#| tbl-cap: "Crosstab of paired initial ratings of delirium severity"

a1 %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(delirium_severity_B, delirium_severity_A)
```

```{r}
#| label: fig-delseverity-heatmap-pre
#| fig-cap: "Heatmap showing agreement of paired initial ratings of delirium severity"

foo <- a1 %>%
  filter(!is.na(delirium_severity_A), !is.na(delirium_severity_B)) %>%
  group_by(delirium_severity_A, delirium_severity_B) %>%
  summarize(n = n()) 

foo %>%
  ggplot(aes(x = delirium_severity_A, y = delirium_severity_B, fill = n)) +
    geom_tile() +
    scale_x_continuous("Delirium Severity (Rater A)", breaks = 0:9, minor_breaks = NULL) +
    scale_y_reverse("Delirium Severity (Rater B)", breaks = 0:9, minor_breaks = NULL) +
    scale_fill_gradient(
      low = "lightgrey",
      high = "black",
      trans = scales::pseudo_log_trans(sigma = 1),
      breaks = c(1, 3, 10, 30, 100, 200),
      name = "Count"
    ) +
    coord_fixed() +
    hrbrthemes::theme_ipsum()

```

```{r}
#| label: fig-delseverity-heatmap-pre-highlighting
#| fig-cap: "Heatmap showing agreement of paired initial ratings of delirium severity (with highlighting)"

goo <- tribble(~x1, ~x2, ~y1, ~y2,
               -0.5,  0.5, -0.5, -0.5,
               -0.5,  1.5,  0.5,  0.5,
                0.5,  2.5,  1.5,  1.5,
                1.5,  3.5,  2.5,  2.5,
                2.5,  4.5,  3.5,  3.5,
                3.5,  5.5,  4.5,  4.5,
                4.5,  6.5,  5.5,  5.5,
                5.5,  7.5,  6.5,  6.5,
                6.5,  8.5,  7.5,  7.5,
                7.5,  9.5,  8.5,  8.5,
                8.5,  9.5,  9.5,  9.5,
               -0.5, -0.5, -0.5,  0.5,
                0.5,  0.5, -0.5,  1.5,
                1.5,  1.5,  0.5,  2.5,
                2.5,  2.5,  1.5,  3.5,
                3.5,  3.5,  2.5,  4.5,
                4.5,  4.5,  3.5,  5.5,
                5.5,  5.5,  4.5,  6.5,
                6.5,  6.5,  5.5,  7.5,
                7.5,  7.5,  6.5,  8.5,
                8.5,  8.5,  7.5,  9.5,
                9.5,  9.5,  8.5,  9.5
               )

foo %>%
  ggplot(aes(x = delirium_severity_A, y = delirium_severity_B, fill = n)) +
    geom_tile() +
    geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), inherit.aes = FALSE, data = goo, 
                 color = "blue", size = 1.5) +
    scale_x_continuous("Delirium Severity (Rater A)", breaks = 0:9, minor_breaks = NULL) +
    scale_y_reverse("Delirium Severity (Rater B)", breaks = 0:9, minor_breaks = NULL) +
    scale_fill_gradient(
      low = "lightgrey",
      high = "black",
      trans = scales::pseudo_log_trans(sigma = 1),
      breaks = c(1, 3, 10, 30, 100, 200),
      name = "Count"
    ) +
    coord_fixed() +
    hrbrthemes::theme_ipsum()

```


```{r}
#| label: fig-delseverity-scatter-pre
#| fig-cap: "Scatterplot showing agreement of paired initial ratings of delirium severity"

a1 %>%
  filter(!is.na(delirium_severity_A), !is.na(delirium_severity_B)) %>%
  ggplot(aes(x = delirium_severity_A, y = delirium_severity_B)) +
    geom_abline(slope = -1, intercept = 0, color = "blue") +
    geom_jitter(alpha=.5) + 
    scale_x_continuous("Delirium Severity (Rater A)", breaks = 0:9, minor_breaks = NULL) +
    scale_y_reverse("Delirium Severity (Rater B)", breaks = 0:9, minor_breaks = NULL) +
    coord_fixed() +
    hrbrthemes::theme_ipsum()

```



```{r}
#| label: tbl-delseverity-cross-post
#| tbl-cap: "Crosstab of paired consensus ratings of delirium severity"

a2 %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(delirium_severity_B, delirium_severity_A)
```

```{r}
#| label: fig-delseverity-heatmap-post
#| fig-cap: "Heatmap showing agreement of paired ratings of delirium severity after consensus process"

foo <- a2 %>%
  filter(!is.na(delirium_severity_A), !is.na(delirium_severity_B)) %>%
  group_by(delirium_severity_A, delirium_severity_B) %>%
  summarize(n = n()) 

foo %>%
  ggplot(aes(x = delirium_severity_A, y = delirium_severity_B, fill = n)) +
    geom_tile() +
    scale_x_continuous("Delirium Severity (Rater A)", breaks = 0:10, minor_breaks = NULL) +
    scale_y_reverse("Delirium Severity (Rater B)", breaks = 0:10, minor_breaks = NULL) +
    scale_fill_gradient(
      low = "lightgrey",
      high = "black",
      trans = scales::pseudo_log_trans(sigma = 1),
      breaks = c(1, 3, 10, 30, 100, 200),
      name = "Count"
    ) +
    coord_fixed() +
    hrbrthemes::theme_ipsum()


```

```{r}
#| label: fig-delseverity-heatmap-post-highlighting
#| fig-cap: "Heatmap showing agreement of paired ratings of delirium severity after consensus process (with highlighting)"

foo %>%
  ggplot(aes(x = delirium_severity_A, y = delirium_severity_B, fill = n)) +
    geom_tile() +
    geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), inherit.aes = FALSE, data = goo, 
                 color = "blue", size = 1.5) +
    scale_x_continuous("Delirium Severity (Rater A)", breaks = 0:10, minor_breaks = NULL) +
    scale_y_reverse("Delirium Severity (Rater B)", breaks = 0:10, minor_breaks = NULL) +
    scale_fill_gradient(
      low = "lightgrey",
      high = "black",
      trans = scales::pseudo_log_trans(sigma = 1),
      breaks = c(1, 3, 10, 30, 100, 200),
      name = "Count"
    ) +
    coord_fixed() +
    hrbrthemes::theme_ipsum()


```

```{r}
#| label: fig-delseverity-scatter-post
#| fig-cap: "Scatterplot showing agreement of paired consensus ratings of delirium severity"

a2 %>%
  filter(!is.na(delirium_severity_A), !is.na(delirium_severity_B)) %>%
  ggplot(aes(x = delirium_severity_A, y = delirium_severity_B)) +
    geom_abline(slope = -1, intercept = 0, color = "blue") +
    geom_jitter(alpha=.5) + 
    scale_x_continuous("Delirium Severity (Rater A)", breaks = 0:9, minor_breaks = NULL) +
    scale_y_reverse("Delirium Severity (Rater B)", breaks = 0:9, minor_breaks = NULL) +
    coord_fixed() +
    hrbrthemes::theme_ipsum()

```

The correlation between rater A and rater B delirium severity ratings (0-9) prior to the consensus process was `r corr_delirium_severity_initial`. After the consensus process, the correlation was `r corr_delirium_severity_consensus`.  The kappa statistic went from `r kap_delirium_severity_initial` to `r kap_delirium_severity_consensus`.


## Delirium presence

```{r}
#| label: tbl-delpresence-cross-pre
#| tbl-cap: "Crosstab of paired initial ratings of delirium presence"
a1 %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(delirium_presence_B, delirium_presence_A)
```


```{r}
#| label: tbl-delpresence-cross-post
#| tbl-cap: "Crosstab of paired consensus ratings of delirium presence"

a2 %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(delirium_presence_B, delirium_presence_A)
```

The correlation between rater A and rater B delirium presence ratings (Yes/No) prior to the consensus process was `r corr_delirium_presence_initial`. After the consensus process, the correlation was `r corr_delirium_presence_consensus`.  The kappa statistic went from `r kap_delirium_presence_initial` to `r kap_delirium_presence_consensus`.



